% Created 2022-09-17 শনি 20:31
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\author{Abhijit Paul}
\date{\textit{<2022-09-17 শনি>}}
\title{My findings on IFIC}
\hypersetup{
 pdfauthor={Abhijit Paul},
 pdftitle={My findings on IFIC},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.5.5)}, 
 pdflang={English}}
\begin{document}

\maketitle
\clearpage \tableofcontents \clearpage


\section{Sources}
\label{sec:orgb46cb09}
\href{https://rakib3004.github.io/Tech-Edu-Assistant/doc/Pdf3/BusinessStudies.html}{rakib vai's collection}\\
\href{https://core.ac.uk/download/pdf/61805073.pdf}{theisis paper on IFIC bank}\\
\section{{\bfseries\sffamily DONE} Introduction to management \& Organization}
\label{sec:org58d3a8c}
\begin{itemize}
\item IFIC as an organization\\
\item How manager's roles are changing in IFIC\\
\end{itemize}
\section{Organization culture \& Environment}
\label{sec:orgde5716a}
\begin{itemize}
\item Omnipotent or symbolic view?\\
\item IFIC's culture\\
\begin{itemize}
\item Dimensions of organization cutlure\\
\item Strong or weak cutlure in IFIC?\\
\item \texttt{Sources of IFIC culture}\\
\item \texttt{Stories, rituals, material symbols, languages}\\
\end{itemize}
\item External Environment for IFIC bank\\
\begin{itemize}
\item \texttt{Spicific (public pressure group, competitors, customers, suppliers)}\\
\item General (inflation, politics,technology, sociocultural)\\
\end{itemize}
\end{itemize}
\section{{\bfseries\sffamily TODO} Managing in a Global Environment}
\label{sec:orge934ab9}
\begin{itemize}
\item \texttt{IFIC is MNC MDC or global company transnational?}\\
\item Global perspective of IFIC\\
\begin{itemize}
\item \texttt{Parochialistic ethnocentril, polycentric or geocentric?}\\
\end{itemize}
\item Some other forms of globalization\\
\begin{itemize}
\item Joint Venture\\
\item Strategic Alliacne\\
\item Foreign Subsidy\\
\end{itemize}
\item Hofstede's framework for assessing culture\\
\end{itemize}
\section{Social Responsibility}
\label{sec:org3eef9b7}
\begin{itemize}
\item \texttt{The greening of management in IFIC?}\\
\href{https://www.ificbank.com.bd/business/sustainable-finance}{how ific is doing greening of management}\\
\item Ethical training?\\
\end{itemize}
\section{Planning}
\label{sec:orgc263d5f}
\begin{itemize}
\item informal or formal\\
\item Types of plans for branch manager\\
\end{itemize}
\section{Organizational Structure}
\label{sec:orge7556bd}
\begin{itemize}
\item Work specialization\\
\item Departmentalization by type\\
\item Chain of command\\
\item Span of control\\
\item Centralized or decentralized?\\
\item Degree of formalization\\
\item Mechanistic or organic organization?\\
\end{itemize}
\section{Group}
\label{sec:org35449dc}
\begin{itemize}
\item Formal informal\\
\item Command task cross-functional self-managed\\
\end{itemize}
\section{Facebook Live}
\label{sec:org0a9b85e}
Salman F Rahman, besorkari shilpo o biniyog bisiyok upodesta\\

IFIC bank amar protibeshi. Paray paray, sobar kache(1000 branches) - IFIC bank\\
12.5k ATM\\
commercial bank\\
one stop service\\
\subsection{Services of IFIC}
\label{sec:org1c46e57}
\subsubsection{IFIC sohoj account}
\label{sec:org8b38282}
sadharon manuser osadharon account\\
only 10 taka te account khola zay\\
khub olpo kagoj lage\\
ek account ei taka joma, loan deya-neya kora zay\\

no checkboi is given as normal people can easily lose checkboi.\\
you can store 300tk 500tk per month, for poor people.\\

during corona, they gave small loans of 20-30k to 30k people\\
\texttt{"Eta ki 16255" - IFIC bank audio}\\

-- KHUDRRO RIN\\
\subsubsection{IFIC amar account}
\label{sec:org108bf39}
\begin{itemize}
\item dainik haar e FDR er moton akorshonio munafa\\
\item so cholti muldhon cash counter e na rekhe lenden kori IFIC account diye, laav er upore laav\\
\end{itemize}


\texttt{subidha zemon i chai, hisab ektai0}\\
\subsubsection{IFIC Home Loan}
\label{sec:org2e9a4f8}
\begin{itemize}
\item semi-paka bari nirmaneo home lona neya zay\\
\item 
\end{itemize}
\subsubsection{One-stop service}
\label{sec:org4b21d88}
\begin{itemize}
\item desh er first one stop service. Account creation, loan, remittance, DPS - everything from the same place\\

23 services to reduce \texttt{cost of per transaction.} Because one person is serving 23 services so cost reduces. So they have to invest a lot in training human resources.\\
\end{itemize}
\subsubsection{Application}
\label{sec:org303c81c}
apps: IFIC amar bank\\

\begin{itemize}
\item send money to any bank without cost\\
\item get 12month statement\\
\item add image of the person you are sending money to\\
\item Separate "hisab/acccount" for each transaction\\
\end{itemize}
\subsubsection{GONO manuser banking sebaguccho}
\label{sec:orgdfa8478}
\begin{itemize}
\item cost of unit per delivery\\
\item risk management\\
\item delivery channel\\
\item Making the digital app strong for ease of reaching to people.\\
\end{itemize}

AGENCY SYSTEM vs UPO-SAKHA System\\

Transitioning delivery channel to app, one-stop service\\

1-2 crore rin dao, suborno gram rin, sohoj rin\\

\texttt{financial inclusion}\\
\subsubsection{Suborno graam}
\label{sec:org7789221}
\begin{itemize}
\item directly give money to farmers, farm owners to ensure that the mophossol bourgeoisie dont always get the loans\\
\end{itemize}
\section{Fintech}
\label{sec:org53fda4c}
5000 people\\
3B Dollar\\
Half-million customers\\

\href{https://www.youtube.com/watch?v=jy7Ug1pm3aQ}{youtube video}\\
\subsection{Strategy}
\label{sec:orgc425e68}
\begin{enumerate}
\item First develop your backbone: Finastra helped in that\\
\item Develop an environment where customer will come to us: BF Teller, FTI, Finastra\\
\item Reaching to customers 24/7: Finastra\\

Small loans required technology to reach to so many people.\\
\end{enumerate}
\section{Code of Conduct, An amazing document}
\label{sec:orgcadd4ad}
\href{https://ificbank.com.bd/public/assets/investor/human-capital.pdf}{Code of conduct doc, includes culture etc}\\
It shows how IFIC trats its employees.\\

The Bank aims to create a culture of continuous development to enable them to grow and succeed throughout their careers.\\

\href{https://www.glassdoor.com/Interview/IFIC-Bank-Interview-Questions-E558323.htm}{IFIC Interview Questions}\\
\section{Management of IFIC Bank}
\label{sec:org54645bd}
Management of IFIC Bank Limited\\
For any financial and non-financial organization, Management are the most valuable and\\
important resources of any kind of organization. And, a well-organize management provides the\\
organization to reach its ultimate goal. Management means planning, organizing, staffing,\\
directing and controlling of all financial and non-financial resources of an organization. Different\\
aspects of management practice in IFIC Bank Limited are discussed below.\\
\begin{enumerate}
\item Planning: IFIC Bank Limited has done its planning within the purview of the corporate plan. The overall planning approach in IFIC Bank Limited is top-down. Each branch can plan according to the goal imposed by the corporate level. It doesn‘t plan independently. And, IFIC Bank Limited has a planning division. This department is mainly responsible for the overall planning.\\
\item Organizing: IFIC Bank Limited is organized as per the existing business locations. It has 114 branches, each of which is a separate entity. Each unit is responsible for its own performance Relationship Manager. He is directly responsible for the performance of their unit. Within each branch it is organized functionally.\\
\item Directing\\
\end{enumerate}
The management approach in IFIC Bank Limited is top-down or authoritative. Every\\
information just seeks through lower management layer.\\
\begin{enumerate}
\item Controlling\\
\end{enumerate}
Works are designed in such a way that one cannot leave without clearing the tasks as he is assigned for a day.  Budgeting, rewarding, punishing, etc. are also practiced as control mechanism.\\

Sitting arrangement in all 12 office is done in a way that the superior can monitor the subordinate all time.\\
Staffing\\
The recruitment in IFIC Bank is done as a ―Probationary Officers‖ for the management level and\\
it has a probation period of one year and their career path is headed towards different managerial\\
jobs.\\
\section{Theisis paper}
\label{sec:orge5da16f}
 Organization Structure and Responsibilities\\
The nine members of the Board of Directors are responsible for the strategic planning and overall policy guidelines of the Bank. Further, there is an Executive Committee of the Board to dispose of urgent business proposals. Besides, there is an Audit Committee in the Board to oversee compliance of major regulatory and operational issues.\\
The CEO and Managing Director, Deputy Managing Directors and Head of Divisions are responsible for achieving business goals and overseeing the day to day operation. The CEO and Managing Director is assisted by a Senior Management Group consisting of Deputy Managing Directors and Head of Divisions who supervise operation of various Divisions centrally and co-ordinates operation of branches.\\
Key issues are managed by a Management Committee headed by the CEO and Managing Director. This facilitates rapid decisions. There is an Asset Liability Committee comprising member of the Senior Executives headed by CEO and Managing Director to look into all operational functions and Risk Management of the Bank.\\
\section{Cultural Events at IFIC}
\label{sec:org04af7cd}
Every year, IFIC Bank arranges welcoming program for the newborn baby of its employees, arranges award giving ceremony for the meritorious children and celebrates Pohela Boishakh, Hemonto Sondhya and Pitha-Utshob. Other events like celebration of International Women’s Day, children’s art competition, participation in corporate sports events are also arranged to ensure greater levels of bonding and engagement among the employees.\\
\end{document}